Substitution rate response to changes in effective population size and protein expression level.

### 2020-06-16 manuscript/figures.tex
Manuscript formatted to MBE guidelines

\begin{document}
	\begin{frame}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	width=\textwidth,
	height=\axisdefaultheight,
	xlabel={$x$},
	ymin=0.0, ymax=5.0,
	samples=200,
	legend entries={$\ln(\frac{1 - x}{x}) + \ln(19)$,
		${\alpha = -118, \gamma = 1,\Ne = 10^{4}}$,
		${\alpha = -118, \gamma = 1,\Ne = 10^{5}}$,
		${\alpha = -15.7, \gamma = 0.1,\Ne = 10^{4}}$,
		$\tiny{\alpha = -15.7, \gamma = 0.1,\Ne = 10^{5}}$,
	},
	legend cell align=left,
	minor tick num=2,
	axis x line=bottom,
	axis y line=left,
	legend style={at={(0.05,0.25)},anchor=south west}
	]
	\addplot[domain=0.1:0.39,line width=2.0pt, color=BLUE]{ ln(19*(1-x)/x) };
	\addplot[name path=A, domain=0.1:0.38, line width=2.0pt, color=RED]{4*10000*1.686*exp(1.686*(-118+300*x))};
	\addplot[name path=B, dashed,domain=0.3:0.37, line width=2.0pt, color=RED]{4*100000*1.686*exp(1.686*(-118+300*x))};
	\addplot[name path=C,domain=0.1:0.39, line width=2.0pt, color=GREEN]{4*10000*0.1*1.686*exp(1.686*(-15.71+30*x))};
	\addplot[name path=D,dashed,domain=0.1:0.35, line width=2.0pt, color=GREEN]{4*100000*0.1*1.686*exp(1.686*(-15.71+30*x))};
	\addplot[fill=RED, opacity=0.2] fill between[ of = A and B];
	\addplot[fill=GREEN, opacity=0.2] fill between[ of = C and D];
	\end{axis}
	\end{tikzpicture}
\end{frame}

@@

\begin{frame}
\begin{figure}[H]
\centering
\begin{tikzpicture}[scale = 1.0]
\begin{axis}[
width=\textwidth,
height=\axisdefaultheight,
ylabel={Fitness $f(x)$},
xlabel={Phenotype $x$},
cycle list name=colors,
domain=0:1,
samples=200,
legend cell align=left,
minor tick num=2,
axis x line=bottom,
axis y line=left,
legend entries={$f(x) = \frac{1}{1 + \e^{\beta(\alpha + \Nsite \gamma x)}}$},
legend style={at={(0.4,0.5)},anchor=south west}
]
\addplot[line width=2.0pt, color=BLUE]{ 1 / (1+exp(1.686*(-12 + 30 * x)))};
\addplot[black]{1.0};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

>>>>

\begin{document}
	\begin{frame}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	width=\textwidth,
	height=\axisdefaultheight*0.75,
	xlabel={$x$},
	ymin=0.0, ymax=5.0,
	samples=200,
	legend entries={$\ln(\frac{1 - x}{x}) + \ln(19)$,
		${\alpha = -118, \gamma = 1,\Ne = 10^{4}}$,
		${\alpha = -118, \gamma = 1,\Ne = 10^{5}}$,
		${\alpha = -15.7, \gamma = 0.1,\Ne = 10^{4}}$,
		$\tiny{\alpha = -15.7, \gamma = 0.1,\Ne = 10^{5}}$,
	},
	legend cell align=left,
	minor tick num=2,
	axis x line=bottom,
	axis y line=left,
	legend style={at={(0.05,0.25)},anchor=south west}
	]
	\addplot[domain=0.2:0.50,line width=2.0pt, color=BLUE]{ ln(19*(1-x)/x) };
	\addplot[name path=A, domain=0.2:0.38, line width=2.0pt, color=RED]{4*10000*1.686*exp(1.686*(-118+300*x))};
	\addplot[name path=B, dashed,domain=0.3:0.37, line width=2.0pt, color=RED]{4*100000*1.686*exp(1.686*(-118+300*x))};
	\addplot[name path=C,domain=0.2:0.383, line width=2.0pt, color=GREEN]{4*10000*0.1*1.686*exp(1.686*(-15.71+30*x))};
	\addplot[name path=D,dashed,domain=0.2:0.35, line width=2.0pt, color=GREEN]{4*100000*0.1*1.686*exp(1.686*(-15.71+30*x))};
	\addplot[fill=RED, opacity=0.2] fill between[ of = A and B];
	\addplot[fill=GREEN, opacity=0.2] fill between[ of = C and D];
	\end{axis}
	\end{tikzpicture}
\end{frame}

@@

\begin{frame}
\begin{figure}[H]
\centering
\begin{tikzpicture}[scale = 1.0]
\begin{axis}[
width=\textwidth,
height=\axisdefaultheight,
ylabel={Fitness},
xlabel={Phenotype},
cycle list name=colors,
domain=0:0.4,
samples=200,
legend cell align=left,
minor tick num=2,
axis x line=bottom,
axis y line=left,
legend entries={$f(x) = \frac{1}{1 + \e^{\beta(\alpha + \Nsite \gamma x)}}$},
legend style={at={(0.4,0.5)},anchor=south west}
]
\addplot[line width=2.0pt, color=BLUE]{ 1 / (1+exp(1.686*(-5 + 10 * x)))};
\addplot[black]{1.0};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}
